An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-24 poly-embed-journal/poly-embed-journal.tex
Refactoring around Lemma 18 and Cor 5

\section{General characteristics of polyhedra}
\label{app:polyhedra}

@@

\begin{definition}[Polyhedron halfspace representation]
	\btw{Def from Ziegler page 28}
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H$
  % = \{H^+_i\}_{i=1}^k$
  presented in the form $P = \cap \H$.
  Here, we say $\H$ is a halfspace representation for $P$.
\end{definition}

@@

Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.
Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$.
Similarly, let $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
%If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

@@

Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$}\\
    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$} \\
    % as the infimum % over $v \in {L(\R)}$ of}\\
    % & & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{definition of $H^+_v$}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & 
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	% The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.

	We now construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
  Since $\hyp(g_{L(\R)}) = \hyp(\risk L_+)$ is a polyhedron, we mae iterate over each of the (finitely many) faces of $\hyp(g_{L(\R)})$.
	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
	There is some $v^{(i)} \in L(\R)$ such that $H_{v^{(i)}}$ supports $\hyp(g_{L(\R)})$ at $x^{(i)}$~\citep[Proposition 3.17]{gallier2008notes}.
	Then $\V = \{v^{(i)}\}_i \subseteq L(\R)$ and is finite by construction.
	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
	% Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
	% Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
	To observe the reverse inequality, consider that $\V$ was constructed via the faces of $\hyp(g_{L(\R)})$, which includes the facets.
	As $x^{(i)}$ on the relative interior of a facet must be defined by a unique supporting hyperplane $v^{(i)}$, we have the set $\H_\V$ must be a superset of the set of hyperplanes defining the facets of $\hyp(g_{L(\R)})$.
	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
	\raft{TODO: We have to slow down here I think.  How do we know $v^{(i)} \in L(\R)$ and that a supporting hyperplane takes the form $H_{v^{(i)}}$?  Also, recall that the whole point of iterating over faces was that we haven't shown the existence of facets yet.  I'm thinking we may want to refactor after all, to show the existence of facets first.}
	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

\subsection{From a finite set of loss vectors to the unique smallest}

The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
In particular, the finiteness of $\V$ gives us a finite halfspace representation $\H$ with which to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
The unique smallest halfspace representation $\H^*\subseteq\H$ will then correspond to a unique $\V^*\subseteq\V$.

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique irredundant $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
  Moreover, $\H_\Y \subseteq \H^*$. 
\end{lemma}
\begin{proof}
	First, we need to show that $\hyp(g_\V)$ is full-dimensional.
	Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.

  Since $\hyp(g_\V)$ is full-dimensional, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).

  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)}. 
\end{proof}

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then
  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii) $F_v := H_v \cap \hyp(g_{\V})$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
  (iii) $\V^* \subseteq \V$.
  (iv) $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{\V})$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
  (iv)   The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  Thus $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
\end{proof}

@@

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\H^*$ is irredundant.
%	WTS
%	(i) $\V^* \subseteq L(\R)$ -- done
%	(ii) $\V^*$ unique and smallest
%	(iii) $g_{L(\R)} = g_{\V^*}$
%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
\end{proof}

@@

	(4) $x \in \pi(F_v^{\hyp(g_{\V^*})})$~.
\end{lemma}
\begin{proof}
	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_\V)}$.
	\begin{align*}
	(1) \quad \quad (x,g_{\V^*}(x)) \in F_v
	&\iff (x,g_{\V^*}(x)) \in \{(x',c) \in \hyp(g_{\V^*}) \mid \inprod{v}{x'} = c\} & \\
	&\iff  \inprod{v}{x} = g_{\V^*}(x) & (2)\\
	&\iff \inprod{v}{x} = \min_{v' \in L(\R)}\inprod{v'}{x} & \\
	&\iff v \in \argmin_{v' \in L(\R)}\inprod{v'}{x}~. & (3)
	\end{align*}
	This covers $1 \iff 2 \iff 3$.

@@

\begin{lemma}\label{lem:levelset-to-extended-levelset}
	Consider $L: \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
\end{lemma}
\begin{proof}
	Fix $r \in \R$ and $c > 0$.
	We have
	\begin{align*}
	p \in \Gamma_r
	&= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Definition of level set} \\
	&= \{p' \in \simplex \mid v \in \argmin_{v' \in L(\R)} \inprod{v'}{p'} \} &  \\
	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in L(\R)} \inprod{v'}{p'} \} & \text {$L$ minimizable} \\
	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_\V(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_{\V^*}$} \\
	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_{\V^*}(p') \} &  \\
	&= \{p' \in \simplex \mid  \inprod{v}{cp'} = g_{\V^*}(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
	\implies cp
	&\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_{\V^*}(x)\} = \bar \Gamma_r~.~
	\end{align*}
\end{proof}

\begin{lemma}\label{lem:extended-levelset-equals-projected-face}
	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_{\V^*})$.
	For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
\end{lemma}
\begin{proof}
	\begin{align*}
	\bar \Gamma_r
	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_\V(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_{\V^*}(x)$}\\
	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_\V(x)\} & \text{$v = L(r)$}\\
	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{\V^*}(x)) \mid \inprod{v}{x} = g_{\V^*}(x)\}$}\\
	\end{align*}
\end{proof}

>>>>

\section{Proving Lemma~\ref{lem:X}}
\label{app:polyhedra}

@@

\begin{definition}[Polyhedron halfspace representation~\citep{ziegler1993lectures}]
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H$
  % = \{H^+_i\}_{i=1}^k$
  presented in the form $P = \cap \H$.
  Here, we say $\H$ is a halfspace representation for $P$.
\end{definition}

@@

Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} \geq c\}$.
%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.
Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$.
Similarly, let $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
%If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

@@

%Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	%Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %%$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$}\\
    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$} \\
    % as the infimum % over $v \in {L(\R)}$ of}\\
    % & & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{definition of $H^+_v$}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & 
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	% The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.

%	We now construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$.
%  Since $\hyp(g_{L(\R)}) = \hyp(\risk L_+)$ is a polyhedron, we mae iterate over each of the (finitely many) faces of $\hyp(g_{L(\R)})$.
%	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
%	There is some $v^{(i)} \in L(\R)$ such that $H_{v^{(i)}}$ supports $\hyp(g_{L(\R)})$ at $x^{(i)}$~\citep[Proposition 3.17]{gallier2008notes}.
%	Then $\V = \{v^{(i)}\}_i \subseteq L(\R)$ and is finite by construction.
%	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
%	% Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
%	% Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
%	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
%	To observe the reverse inequality, consider that $\V$ was constructed via the faces of $\hyp(g_{L(\R)})$, which includes the facets.
%	As $x^{(i)}$ on the relative interior of a facet must be defined by a unique supporting hyperplane $v^{(i)}$, we have the set $\H_\V$ must be a superset of the set of hyperplanes defining the facets of $\hyp(g_{L(\R)})$.
%	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
%	\raft{TODO: We have to slow down here I think.  How do we know $v^{(i)} \in L(\R)$ and that a supporting hyperplane takes the form $H_{v^{(i)}}$?  Also, recall that the whole point of iterating over faces was that we haven't shown the existence of facets yet.  I'm thinking we may want to refactor after all, to show the existence of facets first.}
%	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

\subsection{Finding the unique smallest subset of loss vectors}

%The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
%In particular, the finiteness of $\V$ gives us a finite halfspace representation $\H$ with which to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%The unique smallest halfspace representation $\H^*\subseteq\H$ will then correspond to a unique $\V^*\subseteq\V$.

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  %Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  Consider a loss $L : \reals^d \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
  There is a unique irredundant set $\H^*$ such that $\hyp(g_{L(\R)}) = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_{L(\R)}) \cap H$ is a facet. 
  Moreover, $\H_\Y \subseteq \H^*$. 
\end{lemma}
\begin{proof}
	First, we need to show that $\hyp(g_{L(\R)})$ is full-dimensional.
	Since $g_{L(\R)}$ is nonnegative on $\reals_+^\Y$, $\hyp(g_{L(\R)})$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.

  Since $\hyp(g_{L(\R)})$ is full-dimensional, take $\H^*$ to be the unique irredundant and finite set of closed halfspaces such that $\hyp(g_{L(\R)}) = \H^*$ from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
  Now, $\hyp(g_{L(\R)}) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).

  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g_{L(\R)}(x) > -\infty$.
  The first cannot happen as $g_{L(\R)}$ is concave and finite (namely, nonnegative) at $x = e_y$.
  The second cannot occur as $g_{L(\R)}$ is only finite on $\reals^\Y_+$ by construction with the convex indicator. \raft{TODO: Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?} 6/20/2022: still don't get it, sorry :-)... \jessie{Yeah I changed the sentence entirely.  better? \# burn}}. 
\end{proof}

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  %Suppose we are given a finite set $\V \subset \reals^\Y_+$, and 
  Given a minimizable loss $L: \reals^d \to \reals^\Y_+$ with polyhedral extended risk, consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then
  (i) there is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii) $F_v := H_v \cap \hyp(g_{L(\R)})$ is a facet of $\hyp(g_{L(\R)})$ for each $v\in\V^*$.
  (iv) $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i) Since $\hyp(g_{L(\R)})$ is full-dimensional, the facets of $\hyp(g_{L(\R)})$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_{L(\R)})$ or $H_v \cap \hyp(g_{L(\R)})$.
  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v = H_v \cap \hyp(g_{\V})$ of $\hyp(g_{L(\R)})$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
  (iv)   The result holds if $\hyp(g_{L(\R)}) = \hyp(g_{\V^*})$.
  By construction, $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  Thus $g_{L(\R)}$ can be written as $g_{L(\R)}(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
\end{proof}

@@

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	%Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
	Consider the unique $\V^* \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_{\V^*}$.
	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\H^*$ is irredundant.
%	WTS
%	(i) $\V^* \subseteq L(\R)$ -- done
%	(ii) $\V^*$ unique and smallest
%	(iii) $g_{L(\R)} = g_{\V^*}$
%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
\end{proof}

@@

	(4) $x \in \pi(F_v^{\hyp(g_{\V^*})})$~.
\end{lemma}
\begin{proof}
	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_{L(\R)})}$.
	\begin{align*}
	(1) \quad \quad (x,g_{\V^*}(x)) \in F_v
	&\iff (x,g_{\V^*}(x)) \in \{(x',c) \in \hyp(g_{\V^*}) \mid \inprod{v}{x'} = c\} & \\
	&\iff  \inprod{v}{x} = g_{\V^*}(x) & (2)\\
	&\iff \inprod{v}{x} = \min_{v' \in L(\R)}\inprod{v'}{x} & \\
	&\iff v \in \argmin_{v' \in L(\R)}\inprod{v'}{x}~. & (3)
	\end{align*}
	This covers $1 \iff 2 \iff 3$.

@@

\begin{lemma}\label{lem:levelset-to-extended-levelset}
	Consider $L: \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
\end{lemma}
\begin{proof}
	Fix $r \in \R$ and $c > 0$.
	We have
	\begin{align*}
	p \in \Gamma_r
	&= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Definition of level set} \\
	&= \{p' \in \simplex \mid v \in \argmin_{v' \in L(\R)} \inprod{v'}{p'} \} &  \\
	&= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in L(\R)} \inprod{v'}{p'} \} & \text {$L$ minimizable} \\
	&= \{p' \in \simplex \mid \inprod{v}{p'} = g_{\V^*}(p') \} & \text {Assumption~\ref{assum:V-star-exists-infinite}: $g_{L(\R)} = g_{\V^*}$} \\
	&= \{p' \in \simplex \mid c \inprod{v}{p'} = c g_{\V^*}(p') \} &  \\
	&= \{p' \in \simplex \mid  \inprod{v}{cp'} = g_{\V^*}(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
	\implies cp
	&\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_{\V^*}(x)\} = \bar \Gamma_r~.~
	\end{align*}
\end{proof}

\begin{lemma}\label{lem:extended-levelset-equals-projected-face}
	Consider $L : \R \to \reals^\Y_+, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $v \in L(\R)$, define the face $F_v$ of $\hyp(g_{\V^*})$.
	For any $r\in \R$ with $v = L(r)$, $\bar \Gamma_r = \pi(F_v)$.  
\end{lemma}
\begin{proof}
	\begin{align*}
	\bar \Gamma_r
	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = \risk L_+(x)\} & \text{Definition of $\bar \Gamma_r$}\\
	&= \{x \in \reals^\Y_+ \mid \inprod{L(r)}{x} = g_{L(\R)}(x)\} & \text{Assumption~\ref{assum:V-star-exists-infinite}: $\risk L_+(x) = g_{\V^*}(x)$}\\
	&= \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g_{L(\R)}(x)\} & \text{$v = L(r)$}\\
	&= \pi(F_v) & \text{Since $F_v = \{(x,g_{\V^*}(x)) \mid \inprod{v}{x} = g_{\V^*}(x)\}$}\\
	\end{align*}
\end{proof}
